A Large-scale Study of Polymorphism in R

### 2019-04-04 paper/main.tex
new data and some code
csvs with counts, and fix weird error in paper

\subsection{L1 Types}

@@

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
fixGenes <- function (network, fixIndices, values) {
  ...
  network$fixed[fixIndices] <- as.integer(values)
  ...
\end{lstlisting}}\caption{Example of character/double argument (from {\tt BoolNet} package).}\label{fig:chardbl}\end{figure}%$

In Figure~\ref{fig:matvec}, we see that the function can take in a vector,
but immediately transforms it (transpose, with {\tt t}) into a matrix.  As
an idea, matrix/vector polymorphism seems sensible, as mathematically
vectors are matrices.  R echoes this by making conversion between the two
``types'' easy: \code{as.vector(m)} flattens a matrix \code{m} into a vector
(e.g., \code{as.vector(matrix(2, 2, 2)) == c(2, 2, 2, 2)}), and
\code{as.matrix(v)} builds a {\tt length(v) x 1} matrix (e.g.,
\code{as.matrix(c(1, 2)) == matrix(data=c(1, 2))}).  \AT{TODO fix line break
  in code at end of last sentence}

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
tee <- function (x, theta, D1, D2, phi)  {
    if (is.vector(x)) x <- t(x)
    ...
\end{lstlisting}}\caption{Example of matrix/(\D) argument (from {\tt calibrator} package).}\label{fig:matvec}\end{figure}

%
%
%
%
\section{Related Work}

\AT{Not sure what the best place for this is, but we should discuss these papers somewhere.}

The idea of measuring polymorphism via some program analysis isn't new.
For instance, some work~\cite{aakerblom2015measuring} ... .

More generally, there is an existing literature on analyzing usage patterns
of language features.  For instance, the dynamic features of Smalltalk were
analyzed in some work~\cite{callau2011howdevelopers}, ...

Other analysis work~\cite{milojkovic2017duck} ... .

\section{Conclusions and Future Work}

\bibliographystyle{boilerplate/ACM-Reference-Format}
\bibliography{bib/biblio,bib/jv,bib/r,bib/new}
\end{document}

>>>>

%
%
\subsection{L1 Types}

@@

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
fixGenes <- function (network, fixIndices, values) {
  ...
  network$fixed[fixIndices] <- as.integer(values)
  ...
\end{lstlisting}}\caption{Example of character/double argument (from {\tt BoolNet} package).}\label{fig:chardbl}\end{figure}%$
In Figure~\ref{fig:matvec}, we see that the function can take in a vector,
but immediately transforms it (transpose, with {\tt t}) into a matrix.  As
an idea, matrix/vector polymorphism seems sensible, as mathematically
vectors are matrices.  R echoes this by making conversion between the two
``types'' easy: \code{as.vector(m)} flattens a matrix \code{m} into a vector
(e.g., \code{as.vector(matrix(2, 2, 2)) == c(2, 2, 2, 2)}), and
\code{as.matrix(v)} builds a {\tt length(v) x 1} matrix (e.g.,
\code{as.matrix(c(1, 2)) == matrix(data=c(1, 2))}).  \AT{TODO fix line break
  in code at end of last sentence}
\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
tee <- function (x, theta, D1, D2, phi)  {
    if (is.vector(x)) x <- t(x)
    ...
\end{lstlisting}}\caption{Example of matrix/(\D) argument (from {\tt calibrator} package).}\label{fig:matvec}\end{figure}
%
%
%
%
\section{Related Work}
\AT{Not sure what the best place for this is, but we should discuss these papers somewhere.}
The idea of measuring polymorphism via some program analysis isn't new.
For instance, some work~\cite{aakerblom2015measuring} ... .
More generally, there is an existing literature on analyzing usage patterns
of language features.  For instance, the dynamic features of Smalltalk were
analyzed in some work~\cite{callau2011howdevelopers}, ...
Other analysis work~\cite{milojkovic2017duck} ... .
\section{Conclusions and Future Work}
\bibliographystyle{boilerplate/ACM-Reference-Format}
\bibliography{bib/biblio,bib/jv,bib/r,bib/new}
\end{document}
